%!TEX root = ../dissertation.tex

\begin{otherlanguage}{english}
% \begin{abstract}
% \thispagestyle{plain}
% Your abstract goes here.

% % Keywords
% \begin{flushleft}

% \keywords{my keywords}

% \end{flushleft}
% \end{abstract}

\chapter*{Abstract}
\thispagestyle{empty}

Increasingly more architects are moving from the traditional architectural processes and the classic forms of architectural coding to a modern area called Generative Design. \gls{gd} is the application of computational methods to design architectural structures or objects. In this area, designers write programs that when executed produce geometric models. This movement is clearly visible both in the academia, with current architecture curricula adopting programming courses, and in the industry, with design studios replacing traditional processes with computer applications.  However, for the most users, the transition from \gls{cad} applications to \gls{gd} methods can be quite significant. Therefore, it is important that \gls{gd} systems encourage users to learn, giving them the necessary support to evolve their knowledge and strategies. Unfortunately, the most used systems are not capable of responding to this need because they are old or obsolete, or they do not enforce any good principle of software engineering such as document code. To overcome this problem, this thesis proposes two programming tools for \gls{gd}  systems, namely (1) sketch-program correlation tool that allows architects to use sketches and combining them with code, and (2) immediate feedback tool that accelerates the effect of actions in the program output. We found that while the first tool turns program documentation in a less tiresome task, consequently minimizing the lack of documentation in the  \gls{gd} programs; the second tool enhances the program visualization, creating a new medium that helps people to design programs. This thesis uses Rosetta tool to implement and validate the proposed tools, clearly showing the advantages of this modern programming environment over the most used systems for \gls{gd}.

\begin{flushleft}
\keywords{immediate feedback; image correlation; DrRacket; Rosetta}
\end{flushleft}

\end{otherlanguage}